The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-30 paper/main.tex
cleaning up tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{methods}

@@

Given this laundry-list of assumptions, a general formula for the apparent 
rate density follows:
\begin{align}
\notag
\Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
\left\{ \Gamma_0(r\a, M\a)+ 
\frac{{\rm BF}}{1 - {\rm BF}}
\left[ \int_0^1 \mathrm{d}q \,
       \frac{f(q)}{\mathcal{A}^3}\cdot
       \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}}, 
M\a\right)\,
\right.   
\right. \\
& \quad\quad\quad\quad\quad \left.\left.
+\int_0^1 {\rm d}q\, \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
    \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
{R(qM\a) \over R(M\a)}
q^{-1/3} \right]	\right\},
\label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}=n\b/(n\s+n\b)$ is the volume-limited binary fraction, 
and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms for 
primaries [secondaries], whose functional dependences are omitted for 
notational simplicity.
The dilution terms can be written
\begin{equation}
\mathcal{A}(q, M\a)=\sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
= (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
\mathcal{B}(q, M\a)={R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm 
            sys}(M\a, q)} }
= q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto R^\alpha$ (the 
former are more general).
The rate densities depend on both apparent radius and mass 
because even if the primaries and singles were to have fixed
mass, the mass of secondaries would vary, and so this dependence cannot be 
immediately omitted.

@@

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distances for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Equation~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\,\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If the binary fraction is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this simplifies to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q.
\label{eq:mu_power_laws}
\end{equation}
%which can also be rewritten using the hypergeometric function.
\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform, qualitatively similar to
        Figure~16 of \citet{raghavan_survey_2010}.
        At a given observed transit depth, the searchable binaries in a 
        transit survey are magnitude-limited.
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}
This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance.
Specifically, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability that it has a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Figure~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{results}

\section{Realistic Star and Planet Distributions}
\label{sec:more_complicated}
We will now apply our general equation for the apparent rate 
density (Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in 
regimes of observational interest.
In the following, we write the rate density for each type of star, 
$\Gamma_i(r)$, as the product of a shape function and a constant:
\begin{equation}
\Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where $i=0$ corresponds to single stars, $i=1$ to primaries of 
binaries, and $i=2$ to secondaries of binaries.
The shape function is normalized to unity.
The $Z_i$'s are each system type's occurrence rate $\Lambda_i$, integrated 
over all planetary radii. In other words, they are number of planets per 
single, primary, or secondary star.
We want to consider the effects of varying not only $f_i(r)$ but also the
relative values of the $Z_i$'s.

@@

We are mostly interested in the apparent rate density's radius dependence.
Marginalizing Equation~\ref{eq:general_Gamma_a} over apparent stellar mass, we 
find
that when $Z_0=Z_1=Z_2$,
\begin{align}
X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
\right|_{r\a\rightarrow r} \\
&=
\notag
\frac{1}{1+\mu}
\left[1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
\left(
\int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
\right.
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
\left.\left.
\int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
(1+q^\alpha)^{\frac{3}{2}}
(1+q^{-\alpha})^{\frac{\delta+1}{2}}
\right)\right],
\label{eq:powerlaw_vary_binary}
\end{align}
where $\gamma$ does not appear because of the marginalization over $M\a$.
For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the 
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give 
$(\ldots)\approx 
1.50249$. %171211_model_integrals.nb
For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$; the
relative difference between the apparent rate density and the rate density 
around singles is 4.8\%.
This indicates that considering only twin binaries gave us correct 
intuition: for a power law radius distribution 
($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which there are the same 
number of planets orbiting singles, primaries, and secondaries, binarity 
influences apparent planet occurrence rates around Sun-like stars at the 
$\sim$few percent level.

@@

Further, Figure~\ref{fig:frac_model_3} shows that going from apparent 
radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of detected 
planets with binary companions increases by $\approx 6-12\%$, depending on the 
assumed value of $Z_2/Z_0$. %~\footnote{
%The increase can be derived analytically.
%Let the fraction of total detected planets from primaries at a given 
%apparent radius be $F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm 
%    det}^{\rm tot}$.
%Let the analogous quantity for secondaries be $F_2(r\a)$.
%In the planet-less secondaries case ($F_2(r\a)=0$), one can 
%analyze Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show 
%that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
%check_companion_fractions.py, and LB's notes 2017/12/21.0
%}.
Intuitively speaking, this ``shift'' is a feature of any radius distribution 
that declines at large radii, and flattens below some cutoff $r_{\rm c}$.
This is because (for dilution about primaries)
at apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets will be 
``diluted'' into the given $r\a$, since there are more planets in 
the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.
We compare this prediction with recent observations in 
Section~\ref{sec:discussion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{discussion}

@@

Ignoring these complications, we concentrated in this work on binarity's 
effects on star counts and the apparent radii of detected planets.
Assuming a power law radius distribution, and that no secondaries host HJs,
we found in Section~\ref{sec:model_3} that binarity 
could lead to underestimated HJ rates relative to singles by a multiplicative 
factor of $\approx 1.13$.
We then pointed out in Section~\ref{sec:further_models} that assuming a 
power law radius distribution is probably wrong if one wishes to study the HJ 
rate discrepancy.
If we instead assume a Gaussian radius 
distribution~\citep[following][]{petigura_CKS_2017}, apparent 
HJ rates are {\it greater} than the true rate around singles: the effect goes 
the wrong way.
\begin{comment}
If we believe the assumed power law radius distribution, we can ask whether 
this ``correction factor'' might help resolve the discrepancy.
Explicitly, we ask: what is the probability of \citet{wright_frequency_2012}'s 
result, given a rate drawn from the stated bounds of~\citet{petigura_CKS_2017}?
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account 
for~\citet{guo_metallicity_2017}'s measured metallicity difference between the 
{\it Kepler}\ field and the local solar neighborhood, 9\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply once more by $1.13$ to account for binarity's supposed bias, we 
find that 14\% of RV surveys would detect at least 10 hot Jupiters, still 
suggesting a weak discrepancy.

This suggestion should be taken with caution, because it (likely incorrectly) 
assumes a power law radius distribution.
\end{comment}
The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017} cannot 
possibly be part of a continuous power law. 
Thus binarity is unlikely to resolve the HJ rate discrepancy.

@@

\paragraph{Connecting high resolution imaging to occurrence rates}
One reason to address stellar multiplicity in transit surveys is that it 
changes the interpretation of planet candidates on a system-by-system level.
Consequently, high resolution imaging 
campaigns have measured the multiplicities of almost all {\it Kepler}\ Objects 
of Interest 
\citep{howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
    horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
    law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
    wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been collected 
by~\citet{furlan_kepler_2017}, and they represent an important advance in 
understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram~\citep{furlan_densities_2017}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{conclusion}

@@

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r\a,M\a)$ given the 
true parameters $(r,M)$ is
\begin{equation}
\mathcal{N}_\star^1(r\a, M\a; r, M)
=\int \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
\label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Given this laundry-list of assumptions, a general formula for the
apparent rate density follows:
\begin{align}
    \notag
    \Gamma\a(r\a,M\a) &= {1\over 1+\mu(\mathrm{BF}, M\a)}\times
    \left\{ \Gamma_0(r\a, M\a)+ 
    \frac{{\rm BF}}{1 - {\rm BF}}
    \left[ \int_0^1 \mathrm{d}q \,
           \frac{f(q)}{\mathcal{A}^3}\cdot
           \frac{1}{\mathcal{A}} \Gamma_1\left({r\a\over \mathcal{A}},
    M\a\right)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \frac{f(q)}{\mathcal{A}^3}\cdot \frac{q}{\mathcal{B}}
        \Gamma_2\left({r\a\over \mathcal{B}}, qM\a\right)\cdot
    {R(qM\a) \over R(M\a)}
    q^{-1/3} \right]	\right\},
    \label{eq:general_Gamma_a}
\end{align}
where ${\rm BF}=n\b/(n\s+n\b)$ is the volume-limited binary fraction,
and $\mathcal{A}(q,M\a)$ [$\mathcal{B}(q,M\a)$] are the dilution terms
for primaries [secondaries], whose functional dependences are omitted
for notational simplicity.  The dilution terms can be written
\begin{equation}
    \mathcal{A}(q, M\a)
    = \sqrt{L(M\a) \over L_{\rm sys}(M\a, q)}
    = (1+q^\alpha)^{-1/2},
\end{equation}
and
\begin{equation}
  \mathcal{B}(q, M\a)
  = {R(M\a)\over R(qM\a)}\sqrt{{L(qM\a) \over L_{\rm sys}(M\a, q)} }
  = q^{-1} (1+q^{-\alpha})^{-1/2}
\end{equation}
where the latter equalities assume $L\propto M^\alpha \propto
R^\alpha$ (the former are more general).  The rate densities depend on
both apparent radius and mass because even if the primaries and
singles were to have fixed mass, the mass of secondaries would vary,
and so this dependence cannot be immediately omitted.

@@

\paragraph{Ratio of searchable binaries to singles}

We must also specify the exact form of $\mu$, the ratio of the number
of searchable binary systems to singles.  Given the observed signal
$\delta_{\rm obs}$ and apparent stellar mass $M\a$, recall that the
maximum searchable distances for singles and binaries are proportional
to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm obs}\cdot
[L(M\a)+L(qM\a)]^{1/2}$.  Applying
Equation~\ref{eq:N_searchable_prop},
\begin{equation}
    \mu({\rm BF},M\a)
    = 
    \frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}
    =
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over
        L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
If the binary fraction is independent of $q$, $L \propto M^\alpha$,
and $f(q) \propto q^\beta$, this simplifies to
\begin{equation}
    \mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1
    \left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q.
    \label{eq:mu_power_laws}
\end{equation}
%which can also be rewritten using the hypergeometric function.
\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of
        binary stars, in which the underlying volume-limited
        distribution is uniform, qualitatively similar to Figure~16 of
        \citet{raghavan_survey_2010}.  At a given observed transit
        depth, the searchable binaries in a transit survey are
        magnitude-limited.
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}
This can be understood as a Malmquist bias: at fixed observed transit
depth, for singles and primaries with the same luminosity, binaries
are searchable to a greater distance.  Specifically, the sample of
searchable binaries is magnitude-limited.  Given a searchable binary,
the probability that it has a mass ratio $q$ scales as
\begin{equation}
    p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto
    (1+q^\alpha)^{3/2} q^\beta 
    \label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary
of mass ratio $q$, and the first term is the Malmquist bias when
$L\propto M^\alpha$.  We show this magnitude-limited mass ratio
distribution for the $\beta=0$ case in
Figure~\ref{fig:q_distribn_mag_limited}.  In Monte Carlo simulations
of transit surveys, it is important to draw binaries from a correctly
biased mass-ratio distribution~\citep[\textit{e.g.},][]{
  bakos_hatsouth:_2013,sullivan_transiting_2015, gunther_new_2017}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Realistic Star and Planet Distributions}
\label{sec:more_complicated}

We will now apply our general equation for the apparent rate density
(Equation~\ref{eq:general_Gamma_a}) to study binarity's effects in
regimes of observational interest.  In the following, we write the
rate density for each type of star, $\Gamma_i(r)$, as the product of a
shape function and a constant:
\begin{equation}
    \Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where $i=0$ corresponds to single stars, $i=1$ to primaries of
binaries, and $i=2$ to secondaries of binaries.  The shape function is
normalized to unity.  The $Z_i$'s are each system type's occurrence
rate $\Lambda_i$, integrated over all planetary radii. In other words,
they are number of planets per single, primary, or secondary star.  We
want to consider the effects of varying not only $f_i(r)$ but also the
relative values of the $Z_i$'s.

@@

We are mostly interested in the apparent rate density's radius
dependence.  Marginalizing Equation~\ref{eq:general_Gamma_a} over
apparent stellar mass, we find that when $Z_0=Z_1=Z_2$,
\begin{align}
    X_\Gamma &\equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} 
    \right|_{r\a\rightarrow r} \\
    &=
    \notag
    \frac{1}{1+\mu}
    \left[1 + \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}\times 
    \left(
    \int_0^1 {\rm d}q\,q^\beta (1+q^\alpha)^{\frac{\delta+4}{2}} +
    \right.
    \right. \\
    %isn't latex great?
    &\quad\quad\quad\quad\quad\quad\quad\quad\quad\quad
    \left.\left.
    \int_0^1 {\rm d}q\,q^{\beta+\delta+\frac{5}{3}} 
    (1+q^\alpha)^{\frac{3}{2}}
    (1+q^{-\alpha})^{\frac{\delta+1}{2}}
    \right)\right],
    \label{eq:powerlaw_vary_binary}
\end{align}
where $\gamma$ does not appear because of the marginalization over
$M\a$.  For $\alpha = 3.5$, $\beta=0$, $\gamma=0$, $\delta=-2.92$, the
summed integrals in Equation~\ref{eq:powerlaw_vary_binary} give
$(\ldots)\approx 1.50249$. %171211_model_integrals.nb
For $n\b / (n\b + n\s)=0.44$, this yields $\Gamma\a/\Gamma_0 = 1.048$;
the relative difference between the apparent rate density and the rate
density around singles is 4.8\%.  This indicates that considering only
twin binaries gave us correct intuition: for a power law radius
distribution ($2r_\oplus \lesssim r\a \lesssim 17r_\oplus$) in which
there are the same number of planets orbiting singles, primaries, and
secondaries, binarity influences apparent planet occurrence rates
around Sun-like stars at the $\sim$few percent level.

@@

Further, Figure~\ref{fig:frac_model_3} shows that going from apparent
radii of $2r_\oplus$ to $\approx 1.4r_\oplus$, the fraction of
detected planets with binary companions increases by $\approx 6-12\%$,
depending on the assumed value of $Z_2/Z_0$. %~\footnote{
%The increase can be derived analytically.  Let the fraction of total
%detected planets from primaries at a given apparent radius be
%$F_1(r\a)$, so $F_1(r\a) \equiv n_{\rm det}^1(r\a)/n_{\rm det}^{\rm
%tot}$.  Let the analogous quantity for secondaries be $F_2(r\a)$.  In
%the planet-less secondaries case ($F_2(r\a)=0$), one can analyze
%Eqs~\ref{eq:n_det_0} and~\ref{eq:n_det_1} semi-analytically and show
%that $F_1(2r_\oplus/\sqrt{2})/F_1(2r_\oplus) \approx 1.19$.
%check_companion_fractions.py, and LB's notes 2017/12/21.0 }.
Intuitively speaking, this ``shift'' is a feature of any radius
distribution that declines at large radii, and flattens below some
cutoff $r_{\rm c}$.  This is because (for dilution about primaries) at
apparent radii $r\a < r_{\rm c}/\sqrt{2}$, relatively more planets
will be ``diluted'' into the given $r\a$, since there are more planets
in the undiluted distribution from $r\a$ to $\sqrt{2}r\a$.  We compare
this prediction with recent observations in
Section~\ref{sec:discussion}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Ignoring these complications, we concentrated in this work on
binarity's effects on star counts and the apparent radii of detected
planets.  Assuming a power law radius distribution, and that no
secondaries host HJs, we found in Section~\ref{sec:model_3} that
binarity could lead to underestimated HJ rates relative to singles by
a multiplicative factor of $\approx 1.13$.  We then pointed out in
Section~\ref{sec:further_models} that assuming a power law radius
distribution is probably wrong if one wishes to study the HJ rate
discrepancy.  If we instead assume a Gaussian radius
distribution~\citep[following][]{petigura_CKS_2017}, apparent HJ rates
are {\it greater} than the true rate around singles: the effect goes
the wrong way.
\begin{comment}
  If we believe the assumed power law radius distribution, we can ask
  whether this ``correction factor'' might help resolve the
  discrepancy.  Explicitly, we ask: what is the probability of
  \citet{wright_frequency_2012}'s result, given a rate drawn from the
  stated bounds of~\citet{petigura_CKS_2017}?  In other words, we
  first take the true HJ rate per thousand stars as $\Lambda_{\rm HJ}
  = 5.7 \pm 1.3$, with Gaussian uncertainties.  We then draw from a
  Poisson distribution and compute the probability of detecting at
  least 10 hot Jupiters in a sample of 836 stars.  Without accounting
  for binarity or metallicity, only 4\% of RV surveys would detect at
  least 10 hot Jupiters.  If we multiply $\Lambda_{\rm HJ}$ by $1.2$
  to account for~\citet{guo_metallicity_2017}'s measured metallicity
  difference between the {\it Kepler}\ field and the local solar
  neighborhood, 9\% of RV surveys would detect at least 10 hot
  Jupiters.  If we multiply once more by $1.13$ to account for
  binarity's supposed bias, we find that 14\% of RV surveys would
  detect at least 10 hot Jupiters, still suggesting a weak
  discrepancy.  This suggestion should be taken with caution, because
  it (incorrectly) assumes a power law radius distribution.
\end{comment}
The ``hot Jupiter island'' reported by~\citet{petigura_CKS_2017}
cannot possibly be part of a continuous power law.  Thus binarity is
unlikely to resolve the HJ rate discrepancy.

@@

\paragraph{Connecting high resolution imaging to occurrence rates}
One reason to address stellar multiplicity in transit surveys is that
it changes the interpretation of planet candidates on a
system-by-system level.  Consequently, high resolution imaging
campaigns have measured the multiplicities of almost all {\it Kepler}\
Objects of Interest~\citep{
  howell_speckle_2011,adams_adaptive_2012,adams_adaptive_2013,horch_observations_2012,
  horch_most_2014,lillo-box_multiplicity_2012,lillo-box_high-resolution_2014,dressing_adaptive_2014,
  law_robotic_2014,cartier_revision_2015,everett_high-resolution_2015,gilliland_hubble_2015,
  wang_influence_2015,wang_influence_2015-1,baranec_robo-ao_2016,ziegler_robo-ao_2017}.
The results of these programs have been collected
by~\citet{furlan_kepler_2017}, and they represent an important advance
in understanding the KOI sample's multiplicity statistics.  In
particular, they can be immediately applied to rectify binarity's
effects on the mass-radius diagram~\citep{furlan_densities_2017}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\paragraph{Primaries in binaries}
The number of primaries with apparent parameters $(r\a,M\a)$ given the
true parameters $(r,M)$ is
\begin{equation}
    \mathcal{N}_\star^1(r\a, M\a; r, M)
    = \int 
      \mathrm{d}q\,f(q)\mathcal{N}_{{\rm s}, q}^1(r\a, M\a, q; r, M),
    \label{eq:fancyN_s_1}
\end{equation}
where $f(q)$ is the volume-limited binary mass ratio distribution.
